Text Is All You Need

### 2023-05-04 docs/hes_final/article.qmd
Actually push images for tables

We evaluated the models against a set of common performance metrics (see @fig-best-max-metrics, @fig-best-min-metrics, @fig-roc, 
@fig-prc). Despite conceptual differences in dataset creation and modeling techniques, all three of the described above approaches 
produced comparative results. Each of the models outperformed the other two in a subset of these metrics.

@@

\onecolumn

::: {layout="[[1, 1]]"}

@@

:::

::: {layout="[[1, 1]]"}

@@

![Precision Recall Curve](imgs/fig-prc.png){#fig-prc}

:::
::: {layout="[[1, 1]]"}

@@

:::
::: {layout="[[1, 1]]"}

@@

:::
\twocolumn

>>>>

We evaluated the models against a set of common performance metrics (see @fig-best-max-metrics, @fig-best-min-metrics, @fig-roc). 
Despite conceptual differences in dataset creation and modeling techniques, all three of the described above approaches 
produced comparative results. Each of the models outperformed the other two in a subset of these metrics.

@@

@@

@@

@@

@@
